---
title: "Learning RMarkdown with Shiny at ODSC East 2018 from Jared Lander"
author: "Scott Russell"
date: "May 2, 2018"
output:
  word_document:
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
---

For RMarkdown section 2, global setting for RMarkdown page. 
```{r settings, include=TRUE}
knitr::opts_chunk$set(cache=TRUE)
```

# Markdown Formatting

`<!-- comment with highlighting and hitting Ctrl+Shift+C -->`

## Section One

We started a new section. That is all it takes.

Leaving a blank line before the next text starts a new paragraph.

Hit F7 in RStudio to run spell-check.

## Section Two

Here's section two. Let's create subsections.

### Subsection One

We started a subsection, using two hashtags ( `##` ).

### Subsection Two

Section headings match up to HTML header tags, h1 - h6, so `#` to `######`.

## Formatting Text

Not styling (that's for CSS).

_Emphasized Text_ is done with `_emphasized text_`. Use emphasize so that CSS can be used to define how emphasis is styled. Can also use asterisks `*emphasized text*` instead.

__Strong Text__ is done with `__strong text__`.

___Emphasized and strong text___ is done with `___emphasized and strong text___`.

`unformatted code` is done with backticks ``.

## Lists

### Unordered Lists

Done with `- text` on every line.

- Apple
- Banana
- Orange
- Kiwi
- Durian
- Watermelon

### Ordered Lists

Done with `1. text` or `a. text` on every line. If you want Roman Numerals, that's a CSS change.

1. New York
1. New Jersey
1. Detroit
1. Naples
1. New Haven
1. Rome

a. Pepperoni
b. Broccoli
c. Ricotta
d. Onion
e. Eggplant

### Nested Lists

Can nest ordered and unordered lists within other lists.

1. New York
    1. Coal
    1. Wood
    1. Gas
1. New Jersey
    - Gas
    - Wood
1. Naples

## Links

[My Github](https://github.com/amundsenjunior)

# RMarkdown

Insert R code chunk with `Ctrl+Alt+I`. Can insert other language chunks, to insert in the curly braces (e.g. `{python}`, `{bash}`, or `{sql}`).

Can hit `Ctrl+Enter` in the .Rmd file to run R code
```{r}
1 + 1
```

```{r}
x <- 3
x
```

```{r}
x*2
```

Let's give our chunks names. Add a name after the r language pointer in the head of the chunk: `{r code-name-with-no-spaces}`. They must be unique across the entire document.
```{r simple-code-ex}
x*3+7
```

Let's show the results of a chunk without seein the code, with `{r code-name, echo=FALSE}`.
```{r another-example, echo=FALSE}
5*x + 4
```

## Plots

Let's make a nice plot.
```{r load-ggplot}
library(ggplot2)
```

Add alignment and a caption to the plot, with `{r code-name, fig.align='center', fig.cap='Caption text'}`.

Cache the image creation from the Rmarkdown knitting so it loads faster, with `{r cache=TRUE}`.
```{r plot-diamonds, fig.align='center', fig.cap='A scatterplot of diamond price vs size, color coded according to diamond cut.', cache=TRUE}
ggplot(diamonds, aes(x=carat, y=price, color=cut)) +
    geom_point()
```

